---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# interactive.psplots

<!-- badges: start -->
<!-- badges: end -->

The goal of interactive.psplots is to generate an interactive stacked bar plot
from a phyloseq object. The plot will show the relative abundances of the most 
common taxa and allows the user to specify the number of most abundant taxa as
well as the taxonomic level (e.g. Phylum, Class, Order, etc.). This package may
be useful if you've recently processed sequence data (e.g. 16S) through a pipeline
like mothur or dada2 and would like to quickly create a visualization to probe 
the results and guide further inquiry or visualization direction.

Phyloseq class objects have several components, some of which are optional. This
package requires your phyloseq to include an OTU table, an assigned taxa table,
and a data frame with sample data. *IMPORTANT* this package expects a column in
your sample data to be titled "sample.name". 

The included ps_bar_intr() function requires three inputs (see example below): a phyloseq
object, the taxonomic level desired for visualization (as a string which *must* match
the title of one of the columns in your phyloseq's taxa table), and the number of 
most abundant taxa you would like displayed on the plot. Once the plot generates,
hovering the cursor over the bars will display the corresponing relative abundance, 
taxa name, and sample name.

## Installation

You can install the development version of interactive.psplots from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jlolavesen/interactive.psplots")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(interactive.psplots)

## buildng a simple, nonsensical phyloseq object for example purposes
z <- cbind(c("Archaea","Bacteria"),c("Methyltropha","Bacteriodes"))
colnames(z) <- c("Phylum", "Class")
df <- data.frame(c("A", "B"), c("C", "D"))
colnames(df) <- c("sample.name", "group")
y <- matrix(1:4,nrow=2)
ps <- phyloseq::phyloseq(
  phyloseq::otu_table(y, taxa_are_rows = FALSE),
  phyloseq::tax_table(z),
  phyloseq::sample_data(df))

##generating the interactive plot
ps_bar_intr(ps, "Phylum", 2)
```


